The first high-redshift changing-look quasars

### 2019-12-11 tex/CIV_CLQs.tex
arXiv SUBMITTEDclear

\begin{abstract}
We report on three redshift $z>2$ quasars with dramatic changes in
their \civ\ emission lines, the first ``Changing-Look'' quasars at
high redshift.  This is also the first time the changing-look
behaviour has been seen in a high-ionization emission line.  SDSS
J1205+3422, J1638+2827 and J2228+2201 show interesting behaviour in
their observed optical light curves, and subsequent spectroscopy shows
significant changes in the \civ\ broad emission line, with both line
collapse and emergence being displayed in rest-frame timescales of
$\sim$240-1640 days.  These are very quick changes, especially when
considering virial black hole mass estimates have all three quasars
with $M_{\rm BH} > 10^{9} M_{\odot}$.  Continuum and emission line
measurements from the three quasars show changes in the
continuum-equivalent width plane with the CLQs seen to be on the edge
of the full population distribution, and showing indications of an
intrinsic Baldwin Effect. We put these observations in context with
recent ``state-change'' models, but note that even in their
`low-state', the \civ\ CLQs are above $\sim$10\% in Eddington
luminosity.
\end{abstract}

\begin{keywords}
accretion, accretion discs -- surveys -- quasars: general -- quasars: time-domain: 
\end{keywords}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%
%%   SECTION 1  SECTION 1  SECTION 1  SECTION 1  SECTION 1  SECTION 1  
%%   SECTION 1  SECTION 1  SECTION 1  SECTION 1  SECTION 1  SECTION 1  
%%   SECTION 1  SECTION 1  SECTION 1  SECTION 1  SECTION 1  SECTION 1  
%%
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
Luminous AGN, i.e. quasars, are now seen to significantly vary their
energy output on timescales as short as weeks to months.  This
observation, and the subsequent mismatch in the expected ``viscous''
timescale, which for a 10$^{7}$ M$_{\odot}$ central supermassive black
hole (SMBH) is $\sim$hundreds of years, was noted over 30 years ago
\citep[e.g.][]{Alloin1985}. However, with new photometric light-curve
and repeat spectroscopic data, the desire for a deeper understanding
of AGN accretion disk physics has recently re-invigorated the field
\citep[e.g.][]{Antonucci2018, Lawrence2018, Ross2018, Stern2018}.

The optical continuum variability of quasars has been recognized since
their first optical identification
\citep[e.g.,][]{MatthewsSandage1963, MacLeod2012}.  Dramatic changes
in the broad emission lines (BELs) of quasars has only recently been
identified \citep[e.g., ][]{LaMassa2015}.  Samples of over 100
``Changing Look'' quasars (CLQs) or ``Changing State'' quasars (CSQs)
have now been assembled \citep[e.g.][]{MacLeod2019, Graham2019b}. The
community uses both these terms as a cover for the underlying
physics. For sake of argument, CLQs can potentially be thought of as
the extension to the BELs of quasar continuum variability \citep[e.g.,
][]{MacLeod2012} whereas the CSQs have a `state-transition' similar to
that in Galactic X-ray binaries \citep[][]{NodaDone2018, Ruan2019a}. In
this paper, we use the term `Changing Look', as we are currently
agnostic, and confessedly ignorant, to the underlying physical
processes.

@@

      Line                 & $\lambda$ &  Transition  & Ionization   &  \multicolumn{6}{c}{Transition Levels}                                                                                           & Wavenumber   & $A_{i,j}$                    \\
                              &  / \AA\    & energy / eV &  energy / eV  &    \multicolumn{3}{l}{Lower}    &  \multicolumn{3}{l}{Upper}                                                         & / cm$^{-1}$    & ($\times10^{8}$  / s$^{-1}$)               \\      \hline

@@

      atomic data.  Data from the NIST Atomic Spectra Database
      \citep{Kramida2018, Kramida2019}.  The Transition Energies are
      $E=hc/\lambda$ for the given wavelength. The Ionization Energy is the
      energy required to ionize the given species, e.g. 64.49 eV are needed
      to create a \cv\ ion.  Transitions Level configurations are given in
      standard spectroscopic notation $A_{i,j}$ are transition
      probabilities.  Data from the NIST Atomic Spectra Database
      \citep{Kramida2018, Kramida2019}.}

@@

CLQs to date have primarily been defined according to the
(recombination) Balmer emission line properties with particular
attention paid to the H$\beta$ emission line, observed from optical
spectroscopy. Recent work report on discoveries of \mgii Changing-look
AGN \citep{Guo2019, Homan2019}. However, current CLQ studies have
primarily been at redshifts $z<1$.

While there have been many studies on triply ionized carbon, i.e
\civ, these have tended to focus on broad absorption line quasars
\citep[BAL quasars; see Table 1 of][]{Hemler2019} or the Baldwin Effect
\citep[BEff; ][]{Baldwin1977, Bian2012, Jensen2016,
Hamann2017}\footnote{As noted in \citet{Rakic2017}, two different
types of Baldwin effect are present in the literature: the {\it
global} (or {\it ensemble}) Baldwin Effect, which is an
anti-correlation between the Equivalent Width (EW) of the emission line and the
underlying continuum luminosity of {\it single-epoch} observations of
a {\it large number} of AGN and second, the {\it intrinsic} Baldwin
effect, the same anti-correlation but in an {\it individual, variable}
AGN \citep{PoggePeterson1992}.}.  Dramatic changes in the
collisionally excited broad {\it emission} line (BEL) of \civ\ and
indeed \ciii have not to this point been reported.

\begin{table*}
  \centering
  \begin{tabular}{l l   r ll  r r l}
    \hline 
    \hline 
    \multirow{2}{*}{Object} & \multirow{2}{*}{Redshift} & $g$-band & \multirow{2}{*}{MJD} & \multirow{3}{*}{Instrument} & Exposure      &   SDSS               & \multirow{2}{*}{Notes} \\
                                         &                                        &   (mag)      &                                 &                                             &  Time (secs) &   Plate-FiberID  & \\
    \hline  
                                       & 2.068                              & 18.27          &  53498                   & SDSS                                     &  8057            & 2089-427             & \\
 J120544.7+342252.4     & 2.071                             &                    &  58538                   & DBSP                                     &  1800            &  ---                      &  Average conditions \\
                                       & 2.071                             &                     &  58693                  & DBSP                                      &  2400            &  ---                      &          \\
                                       &                                       &                     &                               &                                              &                      &                               &                               \\
                                      & 2.185                              & 19.77           &  54553                   & SDSS                                     &   4801            &  2948-614              & \\
J163852.9+282707.7     & 2.186                              &                    &  55832                     & BOSS                                    &   3600            &  5201-178            & \\
                                      & 2.182                              &                     &  58583                     & LRIS                                    &  1800              &  ---                      & \\
                                      &                                         &                    &                                 &                                            &                      &                              &                                 \\
                                      & 2.217                               & 19.97          &  56189                    &  BOSS                                    &  2700            &   6118-720          & \\
 J222818.7+220102.9   & 2.222                               &                    &  56960                     & BOSS                                    &  4500            &   7582-790          & eBOSS reobservation \\ 
                                     &  2.222                               &                    &  58693                    &  DBSP                                    & 2400             &    ---                        &    \\
    \hline \hline   
  \end{tabular}
  \caption{Details of our spectroscopic observations.  Redshift errors are
    typically $\pm$0.002.  SDSS, BOSS and eBOSS spectra have
    $\mathcal{R}\sim$2,000.  DBSP: Double Spectrograph on the Palomar
    200-inch telescope.  LRIS: Low Resolution Imaging Spectrometer on Keck
    I 10m telescope.} 
  \label{tab:obs_notes}
\end{table*}

Here, we present new results for three quasars which show dramatic
changes in their \civ\ and \ciii broad emission line properties as
well as in their underlying continuum. These are some of the first
examples of ``Changing Look Quasars'' at high ($z>1$)
redshift. Moreover, these are the first cases for substantial changes
of ions with high ionization potentials (I.P.'s $>$2 Rydberg), thus
linking the ionizing photons to the energetic inner accretion disk,
potentially by inverse Compton scattering of lower energy photons to
higher energies.

Details of the atomic transitions that produce strong rest-frame
UV/optical lines in quasars are given in
Table~\ref{tab:atomic_lines}. In this paper we use the wavelengths of
1548.202 and 1550.774~\AA\ for the \civ\ doublet
\citep{Kramida2018}. For ionisation energies, 47.89 eV (3.519 Ry) is
required for doubly-ionised C~III to become triply-ionised \civ.
64.49 eV (4.74 Ry) is the energy needed to ionize \civ\ itself. This
energy corresponds to a thermal temperature of $T \gtrsim$
4$\times10^{5}$, implying a heating energy source of (soft) X-ray
photons.

\citet{Wilhite2006} examine \civ\ variability in a sample
of 105 quasars observed at multiple epochs by the Sloan Digital Sky
Survey \citep[SDSS;][]{York2000, Stoughton2002, Abazajian2009}.  They
find a strong correlation between the change in the \civ\ line
flux and the change in the line width, but no correlations between the
change in flux and changes in line center and skewness.  These authors
find that the relation between line flux change and line width change
is consistent with a model in which a broad line base varies with
greater amplitude than the line core. The \civ\ lines in these
high-luminosity quasars appear to be less responsive to continuum
variations than those in lower luminosity AGN.

\citet{Richards2011} explored the BEL region in over 30,000 $z > 1.54$
SDSS quasars, concentrating on the properties of the \civ\ emission
line. These authors consider two well-known effects involving the
\civ\ emission line: {\it (i)} the anti-correlation between the \civ\
equivalent widths (EWs) and luminosity (i.e., the Baldwin Effect;
BEff) and {\it (ii)} the blueshifting of the peak of \civ\ emission
with respect to the systemic redshift.  We denote the velocity offset
of emission lines as $V_{\rm off}$ and use the convention that a
positive $V_{\rm off}$ value means the line is blueshifted while a
negative $V_{\rm off}$ value means the line is redshifted.
\citet{Richards2011} find the blueshift of the \civ\ emission line, is
found to be nearly ubiquitous, with a mean shift of $V_{\rm off}
\sim$810 km s$^{-1}$ for radio-quiet (RQ) quasars and $V_{\rm off}
\sim$360 km s$^{-1}$ for radio-loud (RL) objects. \citet{Richards2011}
also find the BEff is present in both the RQ and RL studied samples.
These author conclude that these two \civ\ parameters (EQW and
blueshift) are capturing an important trade-off between ``disk'' and
``wind'' components in the disk-wind model of accretion disks
\citep[e.g.,][]{Murray1995, Elvis2000, Proga2000, Leighly2004b}, with
one dominating over the other depending on the shape of the SED.

Using the multi-epoch spectra of 362 quasars from the Sloan Digital
Sky Survey Reverberation Mapping \citep[SDSS-RM; ][]{Shen2015,
Shen2019} project, \citet{Sun2018} investigate the blueshift of \civ\
emission relative to \mgii emission, and its dependence on quasar
properties. These authors confirm that high-blueshift sources tend to
have low \civ\ EWs, and that the low-EW sources span a range of
blueshift. Other high-ionization lines, such as \heii, also show
similar blueshift properties. The ratio of the line width of \civ\ to
that of \mgii increases with blueshift. \citet{Sun2018} also find that
quasar variability might slightly enhance the connection between the
\civ\ blueshift and EW, though further investigation here is
warranted. There is also the finding that the objects with that
largest blueshifts are less variable and tend to have higher Eddington
ratios. \citet{Sun2018} explain their results these by suggesting that
quasar SEDs have weaker X-ray emission (or at least a larger UV/optical-to-Xray
spectral index, $\alpha_{\rm ox}$) and thus become {\it
softer} with {\it increasing Eddington ratio} along with the presence
of X-ray shielding by the inner accretion disk. However, a high
Eddington ratio alone might be an insufficient condition for the \civ\
blueshift. Recent investigations also include \citet{Meyer2019} and
\citet{Doan2019}. \citet{Dyer2019} provide a detailed analysis of 340
quasars at high-redshift ($1.62<z<3.30$) from the SDSS-RM project,
which we will compare our results to.

%%    P a p e r    O v e r v i e w
The purpose of this paper is, for the first time, to systematically
access and report on the CLQ phenomenon at high ($z>2$)
redshift. While accessing this phenomenon at an earlier cosmic epoch
is somewhat interesting, the main value of this study is we move from
the low-ionization energy Balmer emission line series to the
high-ionization emission lines, in particular \civ\ $\lambda$1549.

This paper is organised as follows. In Section 2, we describe our
sample selection, catalogues, and observational data sets.  In Section
3, we show the high-$z$ quasars and report the line properties for the
quasars at the observed epochs.  We give a very brief theoretical
discussion in Section 4. We present our conclusions in Section 5.  We
report all magnitudes on the AB zero-point system \citep{Oke_Gunn1983,
Fukugita1996} unless otherwise stated. For the WISE bands, $m_{\rm AB}
= m_{\rm Vega} + m$ where $m = (2.699, 3.339)$ for WISE W1 at
3.4$\mu$m and WISE W2 at 4.6$\mu$m, respectively \citep{Cutri2011,
Cutri2013}. We adopt a flat $\Lambda$CDM cosmology with
$\Omega_{\Lambda} = 0.73 $, $\Omega_{\rm M} = 0.27$, and $h =
0.71$. All logarithms are to the base 10.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%    SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2  
%%    SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2  
%%    SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2  
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Data, CLQ Selection and Line measurements}
In this section we present the photometric data used to select the
CLQs, and then give details to the multiwavelength data where we have
it. We then give details of the spectroscopic data including emission
lines measurements.

\subsection{Photometry}
\subsubsection{Optical Photometry}
We use optical data from the Catalina Real-time Transient Survey
\citep[CRTS;][]{Drake2009, Mahabal2011}, the Panoramic Survey
Telescope and Rapid Response System \citep[PanSTARRS;][]{Kaiser2010,
Stubbs2010, Tonry2012, Magnier2013} and the Zwicky Transient Facility
\citep[ZTF;][]{Bellm2019_ZTFOverview}.

The CRTS archive\footnote{http://catalinadata.org} contains the
Catalina Sky Survey data streams from three telescopes -- the 0.7 m
Catalina Sky Survey (CSS) Schmidt and 1.5 m Mount Lemmon Survey (MLS)
telescopes in Arizona and the 0.5 m Siding Springs Survey (SSS)
Schmidt in Australia. CRTS covers up to $\sim$2500 deg$^2$ per night,
with 4 exposures per visit, separated by 10 min. The survey observes
over 21 nights per lunation. The data are broadly calibrated to
Johnson $V$ \citep[see ][for details]{Drake2013} and the current CRTS
data set contains time series for approximately 400 million sources to
$V \sim 20$ above Dec $> -30$ from 2003 to 2016 May (observed with CSS
and MLS) and 100 million sources to $V \sim 19$ in the southern sky
from 2005 to 2013 (from SSS). CRTS has been used to study distant
quasars previously \citep{Graham2014, Graham2015, Graham2015Nature,
Graham2017, Graham2019b}.

@@

In particular we use the Quasar Spectral Fitting (QSFit) software
package presented in \citet{Calderone2017}. This provides luminosity
estimates as well as width, velocity offset and equivalent width of 20
emission lines, including \civ, \ciii and \mgii.  We process and fit
all nine spectra using the lastest version (v1.3.0) of the QSFit
\href{https://qsfit.inaf.it/cat_1.30/onlinefit.php}{online
calculator}. The host galaxy and blended iron emission at rest-frame
optical wavelengths components are automatically disabled when they
can not be constrained by the available data, such as the case for all
our objects (we do not have infrared spectral data).  Power-law
continuum slopes, $\alpha$, where $f_{\lambda} \propto
\lambda^{\alpha}$, are also reported in these catalogues and from
QSFit.

>>>>

\begin{abstract}
We report on three redshift $z>2$ quasars with dramatic changes in
their \civ\ emission lines, the first sample of changing-look quasars
(CLQs) at high redshift.  This is also the first time the
changing-look behaviour has been seen in a high-ionisation emission
line.  SDSS J1205+3422, J1638+2827, and J2228+2201 show interesting
behaviour in their observed optical light curves, and subsequent
spectroscopy shows significant changes in the \civ\ broad emission
line, with both line collapse and emergence being displayed on
rest-frame timescales of $\sim$240-1640 days.  These are rapid
changes, especially when considering virial black hole mass estimates
of $M_{\rm BH} > 10^{9} M_{\odot}$ for all three quasars.  Continuum
and emission line measurements from the three quasars show changes in
the continuum-equivalent width plane with the CLQs seen to be on the
edge of the full population distribution, and showing indications of
an intrinsic Baldwin effect. We put these observations in context with
recent state-change models, and note that even in their observed
low-state, the \civ\ CLQs are generally above $\sim$5\% in Eddington
luminosity. 
\end{abstract}

\begin{keywords}
accretion, accretion discs -- surveys -- quasars: general -- quasars:
time-domain -- quasars: individual (SDSS~J120544.7+342252.4,
SDSS~J163852.9+28270.7.7, SDSS~J222818.7+220102.9)
\end{keywords}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%
%%   SECTION 1  SECTION 1  SECTION 1  SECTION 1  SECTION 1  SECTION 1  
%%   SECTION 1  SECTION 1  SECTION 1  SECTION 1  SECTION 1  SECTION 1  
%%   SECTION 1  SECTION 1  SECTION 1  SECTION 1  SECTION 1  SECTION 1  
%%
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
Luminous AGN, i.e. quasars, are now seen to significantly vary their
energy output on timescales as short as weeks to months.  This
observation, and the subsequent mismatch in the expected viscous
timescale, which for a $10^{7} M_{\odot}$ central supermassive black
hole (SMBH) is $\sim$hundreds of years, was noted over 30 years ago
\citep[e.g.][]{Alloin1985}. However, with new photometric light-curve
and repeat spectroscopic data, the desire for a deeper understanding
of AGN accretion disk physics has recently re-invigorated the field
\citep[e.g.,][]{Antonucci2018, Lawrence2018, Ross2018, Stern2018}.

The optical continuum variability of quasars was recognised since
their first optical identifications
\citep{MatthewsSandage1963}. %MacLeod2012}.  However, dramatic changes
in the broad emission lines (BELs) of quasars was only recently first
identified \citep{LaMassa2015}.  Samples of over 100 ``changing-look''
quasars (CLQs) or ``changing-state'' quasars (CSQs) have now been
assembled \citep[e.g.,][]{MacLeod2019, Graham2019b}. The community
uses both these terms as a cover for the underlying physics. For sake
of argument, CLQs can potentially be thought of as the extension to
the BELs of quasar continuum variability \citep[e.g., ][]{MacLeod2012}
whereas the CSQs have a state-transition, perhaps similar to that seen
in Galactic X-ray binaries \citep[][]{NodaDone2018, Ruan2019a}. In
this paper, we use the term ``changing-look'', as we are currently
agnostic, and confessedly ignorant, to the underlying physical
processes.

@@

      Line                 & $\lambda$ &  Transition  & Ionisation   &  \multicolumn{6}{c}{Transition Levels}                                                                                           & Wavenumber   & $A_{i,j}$                    \\
                              &  / \AA\    & Energy / eV &  Energy / eV  &    \multicolumn{3}{l}{Lower}    &  \multicolumn{3}{l}{Upper}                                                         & / cm$^{-1}$    & / $10^{8}$ s$^{-1}$               \\      \hline

@@

      atomic data from the NIST Atomic Spectra Database
      \citep{Kramida2018, Kramida2019}.  The transition energies are
      $E=hc/\lambda$ for the given wavelength. The ionisation energy is the
      energy required to ionise the given species, e.g., 64.49 eV is needed
      to create a \cv\ ion.  Transition level configurations are given in
      standard spectroscopic notation, with $A_{i,j}$ denoting the transition
      probabilities.}

@@

CLQs to date have primarily been defined according to the
(recombination) Balmer emission line properties with particular
attention paid to the H$\beta$ emission line, observed from optical
spectroscopy. Recent works report on discoveries of \mgii\ changing-look
AGN \citep{Guo2019, Homan2019}. However, current CLQ studies have
primarily been at redshifts $z<1$.

While there have been many studies on triply ionised carbon, i.e.,
\civ, these have tended to focus on broad absorption line quasars
\citep[e.g., Table 1 of][]{Hemler2019} or the Baldwin effect
\citep{Baldwin1977, Bian2012, Jensen2016,
Hamann2017}\footnote{As noted in \citet{Rakic2017}, two different
types of Baldwin effect are present in the literature: {\it (i)} the {\it
global} (or {\it ensemble}) Baldwin effect, which is an
anti-correlation between the emission line equivalent width and the
underlying continuum luminosity of {\it single-epoch} observations of
a {\it large number} of AGN, and {\it (ii)} the {\it intrinsic} Baldwin
effect, the same anti-correlation but in an {\it individual, variable}
AGN \citep{PoggePeterson1992}.}.  Dramatic changes in the
collisionally excited broad {\it emission} line of \civ\ --- and
indeed \ciii\ --- have not to this point been reported.

\begin{table*}
  \centering
  \begin{tabular}{l l   r ll  r r l}
    \hline 
    \hline 
    \multirow{2}{*}{Object} & \multirow{2}{*}{Redshift} & $g$-band & \multirow{2}{*}{MJD} & \multirow{3}{*}{Instrument} & Exposure      &   SDSS               & \multirow{2}{*}{Notes} \\
                                         &                                        &   / mag      &                                 &                                             &  time / sec &   Plate-FiberID  & \\
    \hline  
                                       & 2.068                              & 18.27          &  53498                   & SDSS                                     &  8057            & 2089-427             & Plate quality marginal \\
 J120544.7+342252.4     & 2.071                             &                    &  58538                   & DBSP                                     &  1800            &  ---                      &  Poor conditions \\
                                       & 2.071                             &                     &  58693                  & DBSP                                      &  2400            &  ---                      &  Good conditions        \\
                                       &                                       &                     &                               &                                              &                      &                               &                               \\
                                      & 2.185                              & 19.77           &  54553                   & SDSS                                     &   4801            &  2948-614              & Plate quality good \\
J163852.9+282707.7     & 2.186                              &                    &  55832                     & BOSS                                    &   3600            &  5201-178            & Plate quality good \\
                                      & 2.182                              &                     &  58583                     & LRIS                                    &  1800              &  ---                      & \\
                                      &                                         &                    &                                 &                                            &                      &                              &                                 \\
                                      & 2.217                               & 19.97          &  56189                    &  BOSS                                    &  2700            &   6118-720          & Plate quality good \\
 J222818.7+220102.9   & 2.222                               &                    &  56960                     & eBOSS                                    &  4500            &   7582-790          & Plate quality good \\ 
                                     &  2.222                               &                    &  58693                    &  DBSP                                    & 2400             &    ---                        &    \\
    \hline \hline   
  \end{tabular}
  \caption{Details of our spectroscopic observations.  Redshift errors are
    typically $\pm 0.002$.  SDSS, BOSS, and eBOSS spectra have
    resolving power $\mathcal{R} \equiv \lambda / \Delta \lambda \sim 2000$.  DBSP: Double Spectrograph on the Palomar
    200-inch Hale telescope.  LRIS: Low Resolution Imaging Spectrometer on Keck
    I 10-m telescope.} 
  \label{tab:obs_notes}
\end{table*}

Here, we present new results for three quasars which show dramatic
changes in their \civ\ and \ciii\ broad emission line properties and
underlying continuum. These are some of the first examples of CLQs at
high ($z>1$) redshift. Moreover, these are the first cases for
substantial changes of ions with high ionisation potentials (I.P.'s
$>$2 Rydberg), thus linking the ionizing photons to the energetic
inner accretion disk.

Details of the atomic transitions that produce strong rest-frame
UV/optical lines in quasars are given in
Table~\ref{tab:atomic_lines}. In this paper we use the wavelengths of
1548.202 and 1550.774~\AA\ for the \civ\ doublet
\citep{Kramida2018}. For ionisation energies, 47.89 eV (3.519 Ry) is
required for doubly-ionised C\,{\sc iii} to become triply-ionised
\civ, and 64.49 eV (4.74 Ry) is needed to ionise \civ\ itself. This
energy corresponds to a thermal temperature of $T \gtrsim$
4$\times10^{5}$ K, implying a heating energy source of (soft) X-ray
photons.

\citet{Wilhite2006} examine \civ\ variability in a sample of 105
quasars observed at multiple epochs by the Sloan Digital Sky Survey
\citep[SDSS;][]{York2000, Stoughton2002, Abazajian2009}.  They find a
strong correlation between the change in the \civ\ line flux and the
change in the line width, but no correlations between the change in
flux and changes in line center or skewness.  These authors find that
the relation between line flux change and line width change is
consistent with a model in which a broad line base varies with greater
amplitude than the line core. The \civ\ lines in these high-luminosity
quasars appear to be less responsive to continuum variations than
those in lower luminosity AGN.

\citet{Richards2011} explored the broad emission line region in over
30,000 $z > 1.54$ SDSS quasars, concentrating on the properties of the
\civ\ emission line. These authors consider two well-known effects
involving the \civ\ emission line: {\it (i)} the anti-correlation
between the \civ\ equivalent width (EW) and luminosity (i.e., the
Baldwin effect) and {\it (ii)} the blueshifting of the peak of \civ\
emission with respect to the systemic redshift.  We denote the
velocity offset of emission lines as $V_{\rm off}$ and use the
convention that a positive $V_{\rm off}$ value means the line is
blueshifted while a negative $V_{\rm off}$ value means the line is
redshifted.  \citet{Richards2011} find a blueshift of the \civ\
emission line is nearly ubiquitous, with a mean shift of $\langle
V_{\rm off}\rangle_{\rm RQ} \sim$810 km s$^{-1}$ for radio-quiet (RQ)
quasars and $\langle V_{\rm off}\rangle_{\rm RL} \sim$360 km s$^{-1}$
for radio-loud (RL) objects. \citet{Richards2011} also find the
Baldwin effect is present in both their RQ sample and their RL sample.
They conclude that these two \civ\ parameters (EW and blueshift) are
capturing an important trade-off between disk and wind components in
the disk-wind model of accretion disks \citep[e.g.,][]{Murray1995,
Elvis2000, Proga2000, Leighly2004b}, with one dominating over the
other depending on the shape of the quasar spectral energy
distribution (SED).

Using the multi-epoch spectra of 362 quasars from the SDSS
Reverberation Mapping project \citep[SDSS-RM; ][]{Shen2015, Shen2019},
\citet{Sun2018} investigate the blueshift of \civ\ emission relative
to \mgii\ emission, and its dependence on quasar properties. They
confirm that high-blueshift sources tend to have low \civ\ EWs, and
that the low-EW sources span a range of blueshift. Other
high-ionisation lines, such as \heii, also show similar blueshift
properties. The ratio of the line width of \civ\ to that of \mgii\
increases with blueshift. \citet{Sun2018} also find that quasar
variability might slightly enhance the connection between the \civ\
blueshift and EW, though further investigation here is warranted. They
also find that quasars with the largest blueshifts are less variable
and tend to have higher Eddington ratios, though Eddington ratio alone
might be an insufficient condition for the \civ\ blueshift. Recent
investigations also include \citet{Meyer2019} and
\citet{Doan2019}. \citet{Dyer2019} provide a detailed analysis of 340
quasars at high redshift ($1.62<z<3.30$) from the SDSS-RM project,
which we compare with our results in Section~\ref{sec:theory}.

%%    P a p e r    O v e r v i e w
The purpose of this paper is, for the first time, to systematically
access and report on the CLQ phenomenon at high ($z>2$)
redshift. While accessing this phenomenon at an earlier cosmic epoch
is somewhat interesting, the main value of this study is to move from
the low-ionisation energy Balmer emission line series at rest-frame
optical wavelengths to the high-ionisation emission lines, in
particular \civ\ $\lambda$1549, at rest-frame UV wavelengths.

This paper is organised as follows. In Section 2, we describe our
sample selection, catalogues, and observational data sets.  Section 3
presents the high-redshift quasars and reports their time-variable
line properties.  We provide a brief theoretical discussion in Section
4, and Section~5 presents our conclusions.  We report all magnitudes
on the AB zero-point system \citep{Oke_Gunn1983, Fukugita1996} unless
otherwise stated. For the {\it WISE} bands, $m_{\rm AB} = m_{\rm Vega}
+ m$ where $m = 2.699$ and 3.339 for {\it WISE} W1 (3.4$\mu$m) and W2
(4.6$\mu$m), respectively \citep{Cutri2011, Cutri2013}. We adopt a
flat $\Lambda$CDM cosmology with $\Omega_{\Lambda} = 0.73 $,
$\Omega_{\rm M} = 0.27$, and $h = 0.71$. All logarithms are to the
base 10.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%    SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2  
%%    SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2  
%%    SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2  
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{CLQ Selection and Line Measurements}
In this section we present the photometric data used to select the
CLQs, and then give details to the multiwavelength data where we have
it. We then give details of the spectroscopic data including emission
lines measurements.

\subsection{Photometry}
\subsubsection{Optical Photometry}
We use optical data from the Catalina Real-time Transient Survey
\citep[CRTS;][]{Drake2009, Mahabal2011}, the Panoramic Survey
Telescope and Rapid Response System \citep[PanSTARRS;][]{Kaiser2010,
Stubbs2010, Tonry2012, Magnier2013}, and the Zwicky Transient Facility
\citep[ZTF;][]{Bellm2019_ZTFOverview}.

The CRTS archive\footnote{http://catalinadata.org} contains the
Catalina Sky Survey data streams from three telescopes -- the 0.7-m
Catalina Sky Survey (CSS) Schmidt and 1.5-m Mount Lemmon Survey (MLS)
telescopes in Arizona, and the 0.5-m Siding Springs Survey (SSS)
Schmidt in Australia. CRTS covers up to $\sim$2500 deg$^2$ per night,
with four exposures per visit, separated by 10 min. The survey observes
over 21 nights per lunation. The data are broadly calibrated to
Johnson $V$ \citep[for details, see][]{Drake2013} and the current CRTS
data set contains time series for approximately 400 million sources to
$V \sim 20$ above Dec $> -30$ from 2003 to 2016 May (observed with CSS
and MLS) and 100 million sources to $V \sim 19$ in the southern sky
from 2005 to 2013 (from SSS). CRTS has been extensively used to study 
quasar variability \citep[e.g.,][]{Graham2014, Graham2015, Graham2015Nature,
Graham2017, Graham2019b, Stern2017, Stern2018, Ross2018}.

@@

In particular, we use the Quasar Spectral Fitting (QSFit) software
package presented in \citet{Calderone2017}. This provides luminosity
estimates as well as width, velocity offset and EW of 20 emission
lines, including \civ, \ciii, and \mgii.  We process and fit all nine
spectra using the lastest version (v1.3.0) of the QSFit
\href{https://qsfit.inaf.it/cat_1.30/onlinefit.php}{online
calculator}. The host galaxy and blended iron emission at rest-frame
optical wavelengths components are automatically disabled when they
can not be constrained by the available data, as is the case for all
our quasars.  Power-law continuum slopes, $\alpha$, where $f_{\lambda}
\propto \lambda^{\alpha}$, are also reported in these catalogues and
from QSFit.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3  
%%   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3  
%%   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3  
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}
\subsection{Photometric and Overall Spectral Evolution}
Figure~\ref{fig:civ_clqs} presents the optical and mid-infrared light
curves for three high-redshift CLQ quasars.  Figure~\ref{fig:civ_clqs}
also indicates the spectra for each epoch with vertical dashed lines
in the light curves.
